\Large \bf Web-based Data Analytics in Haskell

### 2011-12-17 paper/paper.tex
Switched from CHI to USENIX latex template

\documentclass{chi2009}
\usepackage{times}
\usepackage{url}
\usepackage{graphics}
\usepackage{color}
\usepackage[pdftex]{hyperref}
\hypersetup{%
pdftitle={Web-based Data Analytics in Haskell},
pdfauthor={Drew Haven, Eric Stratmann},
pdfkeywords={haskell, analytics},
bookmarksnumbered,
pdfstartview={FitH},
colorlinks,
citecolor=black,
filecolor=black,
linkcolor=black,
urlcolor=black,
breaklinks=true,
}
\newcommand{\comment}[1]{}
\definecolor{Orange}{rgb}{1,0.5,0}
\newcommand{\todo}[1]{\textsf{\textbf{\textcolor{Orange}{[[#1]]}}}}

@@

\pagenumbering{arabic}  % Arabic page numbers for submission.  Remove this line to eliminate page numbers for the camera ready copy

\begin{document}
% to make various LaTeX processors do the right thing with page size
\special{papersize=8.5in,11in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\setlength{\pdfpageheight}{\paperheight}
\setlength{\pdfpagewidth}{\paperwidth}

% use this command to override the default ACM copyright statement 
% (e.g. for preprints). Remove for camera ready copy.
\toappear{CS240 Class Project}

\title{FOOBAR: Web-based Data Analytics in Haskell}
\numberofauthors{2}
\author{
  \alignauthor Drew Haven\\
    \affaddr{Stanford University}\\
    \email{drew.haven@gmail.com}
  \alignauthor Eric Stratmann\\
    \affaddr{Stanford University}\\
    \email{eric.stratmann@gmail.com}
}

@@

\bibliographystyle{abbrv}
\bibliography{paper}

>>>>

\documentclass[letterpaper,twocolumn,9pt]{article}
\usepackage{usenix,epsfig,endnotes,url,verbatim,array,fancyvrb,graphicx,grffile}

@@

\begin{document}
\title{\Large \bf Web-based Data Analytics in Haskell}

%don't want date printed
\date{}
%make title bold and 14 pt font (Latex default is non-bold, 16 pt)

%for single author (just remove % characters)
\author{
{\rm Drew Haven, Eric Stratmann}\\
\{drew.haven, eric.stratmann\}@gmail.com
% copy the following lines to add more authors
% \and
% {\rm Name}\\
%Name Institution
} % end author

@@

{\footnotesize \bibliographystyle{acm}
\bibliography{paper.bib}}
